Cycles of the logistic map

### 2013-05-27 doc/pc.tex
pc-ijbc: remove figure and tables

At the intersection,
  the shorter $d$-cycle is branched or ``bifurcated''
  by $(n/d)$-fold to the $n$-cycle.
%
The simplest example is the first bifurcation point
  at $R = 3/4$ for $d = 1, n = 2$,
  where the fixed point \refeq{xr1}
  bifurcates to
  the 2-cycle \refeq{xr2}.
%[recall the $\lambda = -1$ case in \refeq{xr1}
%  and $\lambda = +1$ case in \req{xr2} in \refsec{examples}];
The second bifurcation point at $R=5/4$ for $d = 2, n = 4$ is similar,
  cf. \refsec{examples}.

We will show below that such branching can only happen
  at the onset of the $n$-cycle, where $\lambda = 1$.
%
Further, with a real $R$, only a two-fold branching is possible,
  but a complex $R$ allows higher-fold branchings.

@@

\bibitem{huang}
  Y. N. Huang
  Determination of the stable periodic orbits for the Henon map by analytical method,
  \textit{Chin. Phys. Lett.}
  \textbf{2},
  97--100
  (1985).

>>>>

At the intersection,
  the shorter $d$-cycle undergoes
  a $(n/d)$-tupling to become the $n$-cycle.
%
The simplest example is the first bifurcation point
  at $R = 3/4$ for $d = 1, n = 2$,
  where the fixed point \refeq{xr1}
  bifurcates to
  the 2-cycle \refeq{xr2}.
%[recall the $\lambda = -1$ case in \refeq{xr1}
%  and $\lambda = +1$ case in \req{xr2} in \refsec{examples}];
The second bifurcation point at $R=5/4$ for $d = 2, n = 4$ is similar,
  cf. \refsec{examples}.

We will show below that such tupling can only happen
  at the onset of the $n$-cycle, where $\lambda = 1$.
%
Further, with a real $R$, only a two-fold tupling is possible,
  but a complex $R$ allows higher-fold tuplings.

@@

\bibitem{huang}
  Y. N. Huang
  Determination of the stable periodic orbits for the H\'enon map by analytical method,
  \textit{Chin. Phys. Lett.}
  \textbf{2},
  97--100
  (1985).
